---
title: "CMSY Report"
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

`r if(!is.null(params$cmsy$method)){"#Cmsy method report

The upper left panel shows catches relative to the estimate of MSY, with indication of 95% confidence limits in grey. The upper right panel shows the development of relative total biomass (B/Bmsy), with the grey area indicating uncertainty. The lower left graph shows relative exploitation (F/Fmsy), with Fmsy corrected for reduced recruitment below 0.5 Bmsy. The lower-right panel shows the trajectory of relative stock size (B/Bmsy) over relative exploitation (F/Fmsy).

"}`

```{r echo=FALSE, out.width='100%'}
cat(params$cmsy$method$textRaw, sep = '\n')
```
`r if(!is.null(params$cmsy$method)){"##Output Graphs

Panel A shows in black the time series of catches and in blue the three-years moving average with indication of highest and lowest catch, as used in the estimation of prior biomass by the default rules. Panel B shows the explored r-k log space and in dark grey the r-k pairs which were found by the CMSY model to be compatible with the catches and the prior information. Panel C shows the most probable r-k pair and its approximate 95% confidence limits in blue. Panel D shows in blue the biomass trajectory estimated by CMSY. Dotted lines indicate the 2.5th and 97.5th percentiles. Vertical blue lines indicate the prior biomass ranges. Panel E shows in blue the harvest rate from CMSY. Panel F shows the Schaefer equilibrium curve of catch/MSY relative to B/k, here indented at B/k < 0.25 to account for reduced recruitment at low stock sizes. The blue dots are scaled by CMSY estimates.

"}`
```{r echo=FALSE, out.width='100%'}
knitr::include_graphics( if(Sys.info()[["sysname"]] == "Windows") {paste(gsub("\\\\", "/", params$cmsy$method$analisysChart)) } else { paste(params$cmsy$method$analisysChart)} )
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics( if(Sys.info()[["sysname"]] == "Windows") {paste(gsub("\\\\", "/", params$cmsy$method$managementChart)) } else { paste(params$cmsy$method$managementChart) } )
```

******
## Input parameters  
### Data selection

**Input File** : `r input$fileCmsy$name`

**Stock selected** : `r input$stock`

**Select year range of analysis** : `r min(input$CMSY_years_selected)` to `r max(input$CMSY_years_selected)`

**Years over which to calculate catchability** : `r min(input$CMSY_years_q)` to `r max(input$CMSY_years_q)`

### Resiliance

**Resiliance rate** : `r min(input$resiliance)` to `r max(input$resiliance)`

### Deplation

**Starting depletion range (B/k)** : `r min(input$stb)` to `r max(input$stb)`

**Ending deplation range (B/k)** : `r min(input$endb)` to `r max(input$endb)`

**Does the catch time series have an intermediate year where biomass is particulary high or low?** : `r if(!is.null(input$cmsy_checkbox_intb)){if(input$cmsy_checkbox_intb){"Yes"}else{"No"}}else{"No"}`

`r if(!is.null(input$cmsy_checkbox_intb)){if(input$cmsy_checkbox_intb){paste0("**Intermediate year** : ", input$int.yr)}else{}}else{}`

`r if(!is.null(input$cmsy_checkbox_intb)){if(input$cmsy_checkbox_intb){paste0("**Relative biomass at an intermediate year** : ",min(input$intb)," to ",min(input$intb))}else{}}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("### Advanced use")}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Biomass biological limit (Blim)** : ",input$blim)}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Biomass precautionary value (Bpa)** : ",input$bpa)}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Biomass maximum sustainable yield (BMSY)** : ",input$bmsy)}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Biomass at 40% over the unfished level ( B40% )** : ",input$b40)}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Maximum Sustainable Yield ( MSY )** : ",input$msy)}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Spawning Stock Biomass at MSY ( SSBMSY )** : ",input$msyBTrigger)}else{}`


`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Fishing mortality at Maximum Sustainable Yield ( FMSY )** : ",input$fmsy)}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Fishing mortality biological limit ( Flim )** : ",input$flim)}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Fishing mortality precautionary value ( Fpa )** : ",input$fpa)}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Fishing mortality at overfishing level ( Fofl )** : ",input$fofl)}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Last known exploitation rate** : ",input$last_f)}else{}`

`r if(!is.null(input$cmsy_checkbox_comparison)){paste0("**Natural mortality ( M )** : ",input$m)}else{}`


