---
title: "CMSY Report"
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

`r if(!is.null(params$cmsy$method)){"#Cmsy method report

The upper left panel shows catches relative to the estimate of MSY, with indication of 95% confidence limits in grey. The upper right panel shows the development of relative total biomass (B/Bmsy), with the grey area indicating uncertainty. The lower left graph shows relative exploitation (F/Fmsy), with Fmsy corrected for reduced recruitment below 0.5 Bmsy. The lower-right panel shows the trajectory of relative stock size (B/Bmsy) over relative exploitation (F/Fmsy).

"}`

```{r echo=FALSE, out.width='100%'}
cat(params$cmsy$method$textRaw, sep = '\n')
```
`r if(!is.null(params$cmsy$method)){"##Output Graphs

Panel A shows in black the time series of catches and in blue the three-years moving average with indication of highest and lowest catch, as used in the estimation of prior biomass by the default rules. Panel B shows the explored r-k log space and in dark grey the r-k pairs which were found by the CMSY model to be compatible with the catches and the prior information. Panel C shows the most probable r-k pair and its approximate 95% confidence limits in blue. Panel D shows in blue the biomass trajectory estimated by CMSY. Dotted lines indicate the 2.5th and 97.5th percentiles. Vertical blue lines indicate the prior biomass ranges. Panel E shows in blue the harvest rate from CMSY. Panel F shows the Schaefer equilibrium curve of catch/MSY relative to B/k, here indented at B/k < 0.25 to account for reduced recruitment at low stock sizes. The blue dots are scaled by CMSY estimates.

"}`
```{r echo=FALSE, out.width='100%'}
knitr::include_graphics(c(params$cmsy$method$analisysChart))
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics(c(params$cmsy$method$managementChart))
```

******
## Input parameters  
Input File: `r input$fileCmsy$name`  
  
Stock: `r input$stock`  
Min of year: `r input$minOfYear`  
Max of year: `r input$maxOfYear`  
Start year: `r input$startYear`  
End year: `r input$endYear`  
FLim: `r input$flim`  
FPA: `r input$fpa`  
BLIM: `r input$blim`  
BPA: `r input$bpa`  
BMSY: `r input$bmsy`  
FMSY: `r input$fmsy`  
MSY: `r input$msy`  
MSY B trigger: `r input$msyBTrigger`  
B40: `r input$b40`  
M: `r input$m`  
FOFL: `r input$fofl`  
Last F: `r input$last_f`  
Resiliance: `r input$resiliance`  
r low: `r input$r.low`  
r hi: `r input$r.hi`  
stb low: `r min(input$stb)`  
stb hi: `r max(input$stb)`  
int year: `r input$int.yr`  
intb low: `r input$intb.low`  
intb hi: `r input$intb.hi`  
endb low: `r min(input$endb)`  
endb hi: `r max(input$endb)`  
q start: `r input$q.start`  
q end:: `r input$q.end`  
btype: `r input$btype`  

