---
title: "CMSY Report"
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

`r if(!is.null(params$cmsy$method)){"#Cmsy method report"}`

```{r echo=FALSE, out.width='100%'}
cat(params$cmsy$method$textRaw, sep = '\n')
```
`r if(!is.null(params$cmsy$method)){"##Output Graphs"}`
```{r echo=FALSE, out.width='100%'}
knitr::include_graphics(c(params$cmsy$method$analisysChart))
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics(c(params$cmsy$method$managementChart))
```

******
## Input parameters  
Input File: `r input$file1$name`  
  
Stock: `r input$stock`  
Min of year: `r input$minOfYear`  
Max of year: `r input$maxOfYear`  
Start year: `r input$startYear`  
End year: `r input$endYear`  
FLim: `r input$flim`  
FPA: `r input$fpa`  
BLIM: `r input$blim`  
BPA: `r input$bpa`  
BMSY: `r input$bmsy`  
FMSY: `r input$fmsy`  
MSY: `r input$msy`  
MSY B trigger: `r input$msyBTrigger`  
B40: `r input$b40`  
M: `r input$m`  
FOFL: `r input$fofl`  
Last F: `r input$last_f`  
Resiliance: `r input$resiliance`  
r low: `r input$r.low`  
r hi: `r input$r.hi`  
stb low: `r input$stb.low`  
stb hi: `r input$stb.hi`  
int year: `r input$int.yr`  
intb low: `r input$intb.low`  
intb hi: `r input$intb.hi`  
endb low: `r input$endb.low`  
endb hi: `r input$endb.hi`  
q start: `r input$q.start`  
q end:: `r input$q.end`  
btype: `r input$btype`  

