---
title: "Length-based stock assessment with TropFishR"
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---


```{r echo=FALSE,results='asis'}
        cat("<p> **Figure 1**: Uploaded length-frequency distributions per sampling time (x axis). Panel A shows the raw data, while panel B shows the restructured data. This means after subtracting the moving average (MA) of the count in each length class. The combination of bin size and MA critically affects the separation of peaks (i.e. potential cohorts) in the dataset and thus the estimation of growth parameters by ELEFAN. Blue shading indicates a high count per length bin (panel A) and a high positive value (panel B). Red shading indicates a negative value (only panel B). A good bin size value reduces noise in the data by aggregation. A good MA value leads to visually distinct peaks in particular among small length classes.</P>")
```


## Growth plot

```{r echo=FALSE}
        par(mfrow = c(2,1), mar = c(1,4,0,1), oma = c(3,1,1,0))
        plot(elefan_ga$dataExplo$lfqbin, Fname = "catch", date.axis = "")
        lt <- lfqFitCurves(lfq = elefan_ga$dataExplo$lfqbin,
                           par=as.list(elefan_ga$results$resGA$par),
                           draw = TRUE, lty = 1, col = "dodgerblue2", lwd=2.5)
        legend("topleft",legend=as.expression(bquote(bold("A"))),
               x.intersp = -0.3, y.intersp = 0.3, cex=1.3, bg = "white")
        plot(elefan_ga$dataExplo$lfqbin, Fname = "rcounts")
        lt <- lfqFitCurves(lfq = elefan_ga$dataExplo$lfqbin,
                           par=as.list(elefan_ga$results$resGA$par),
                           draw = TRUE, lty = 1, col = "dodgerblue2", lwd=2.5)
        legend("topleft",legend=as.expression(bquote(bold("B"))),
               x.intersp = -0.3, y.intersp = 0.3, cex=1.3, bg= "white")
```

```{r echo=FALSE,results='asis'}
        cat("<p> **Figure 2**: Uploaded raw (A) and restructured (B) length-frequency data with overlaid von Bertalanffy growth (VBG) curves fitted by ELEFAN with genetic algorithm. Ideally, the growth curves overlay with length bins with a high count or high positive value (blue shading) for raw (A) and restructured (B) data, respectively.</p>")
```

## ELEFAN fit plot
```{r echo=FALSE}
        par(mar=c(5,5,2,1))
        ## GA::plot.ga()
        cex.points = 0.7
        col = c("green3", "dodgerblue3",
                adjustcolor("green3", alpha.f = 0.1))
        pch = c(16, 1)
        lty = c(1,2)
        legend = TRUE
        grid = graphics:::grid
        object <- elefan_ga$results$resGA$gafit
        is.final <- !(any(is.na(object@summary[, 1])))
        iters <- if (is.final) 1:object@iter else 1:object@maxiter
        summary <- object@summary
        ylim <- c(max(apply(summary[, c(2, 4)], 2,
                            function(x) min(range(x, na.rm = TRUE, finite = TRUE)))),
                  max(range(summary[,1], na.rm = TRUE, finite = TRUE)))
        plot(iters, summary[, 1], type = "n", ylim = ylim, xlab = "Generation",
             ylab = "Fitness value (Rn)")
        if (is.final & is.function(grid)) grid(equilogs = FALSE)
        points(iters, summary[, 1], type = ifelse(is.final, "o","p"),
               pch = pch[1], lty = lty[1], col = col[1], cex = cex.points)
        points(iters, summary[, 2], type = ifelse(is.final, "o","p"),
               pch = pch[2], lty = lty[2], col = col[2], cex = cex.points)
        if(is.final){
            polygon(c(iters, rev(iters)), c(summary[, 4], rev(summary[,1])), border = FALSE, col = col[3])
        }else{
            title(paste("Iteration", object@iter), font.main = 1)
        }
        if(is.final & legend){
            inc <- !is.na(col)
            legend("bottomright", legend = c("Best", "Mean", "Median")[inc],
                   col = col[inc], pch = c(pch, NA)[inc],
                   lty = c(lty, 1)[inc], lwd = c(1, 1, 10)[inc],
                   pt.cex = c(rep(cex.points, 2), 2)[inc], inset = 0.02)
        }
```

```{r echo=FALSE,results='asis'}
        cat("<p> **Figure 3**: Score graph of ELEFAN with genetic algorithm. Fitness value (y axis) corresponds here to the score value of ELEFAN (Rn) and in the lingo of genetic algorithm 'Generation' (x axis) refers to the iteration.  Ideally, the number of iterations (or generations) is large enough, so that there are no large jumps visible during the last iterations of the best and average score value.</p>")
```

## Catch curve plot

```{r echo=FALSE}
        resCC <- elefan_ga$results$resCC
        ind <- resCC$reg_int[1]:resCC$reg_int[2]
        par(mar=c(5,5,2,1))
        plot(resCC$t_midL[-ind], resCC$lnC_dt[-ind],
             xlab = "Relative age [years]", ylab = "ln(C/dt)",
             cex=1.4)
        points(resCC$t_midL[ind], resCC$lnC_dt[ind],
               col = "dodgerblue2", pch = 16, cex=1.4)
        abline(resCC$linear_mod, lwd=2.5, col = "dodgerblue2")
        box()
```

```{r echo=FALSE,results='asis'}
        cat("<p> **Figure 4**: Logarithm of catch per length interval against relative age. Blue points correspond to points used in the regression analysis (blue line) of the catch curve for the estimation of total mortality (Z), which corresponds to the slop of the displayed regression line. The selection of points is automatic and based on a list of expert recommendations.</p>")
```


## Selectivity plot

```{r echo=FALSE}
        L50 <- elefan_ga$results$L50
        L75 <- elefan_ga$results$L75
        slist <- list(selecType = "trawl_ogive",
                      L50 = L50, L75 = L75)
        lt <- seq(0, 1.5 * max(elefan_ga$results$lfqbin$midLengths), 0.01)
        sest <- TropFishR::select_ogive(slist, Lt = lt)
        par(mar=c(5,5,2,1))
        plot(lt, sest, ty='n', lwd=2,
             xlab = "Length", ylab = "Probability of capture")
        tmp <- TropFishR::select_ogive(slist, Lt = L50)
        segments(L50, -1, L50, tmp, lty = 2, lwd=1.5, col="grey60")
        segments(-10, tmp, L50, tmp, lty = 2, lwd=1.5, col="grey60")
        tmp <- TropFishR::select_ogive(slist, Lt = L75)
        segments(L75, -1, L75, tmp, lty = 3, lwd=1.5, col="grey60")
        segments(-10, tmp, L75, tmp, lty = 3, lwd=1.5, col="grey60")
        lines(lt, sest, lwd=2.5, col="dodgerblue2")
        legend("bottomright", legend = c("Selection ogive","L50","L75"),
               lty = c(1,2,3), col=c("dodgerblue2","grey60","grey60"),
               lwd=c(2,1.5,1.5))
        box()
```

```{r echo=FALSE,results='asis'}
        if(input$select == "Estimate" || (input$l50_user == 0 && input$l75_user == 0) || (input$l50_user == 0 && input$wqs_user == 0)){
            cat("<p> **Figure 5**: Estimated logistic gear selectivity as the probability of capture (y axis) at length (x axis). Displayed selection ogive is used for the yield per recruit analysis (YPR).</p>")
        }else{
            cat("<p> **Figure 5:** Provided logistic gear selectivity as the probability of capture (y axis) at length (x axis). Displayed selection ogive is used for the yield per recruit analysis (YPR).</p>")
        }
```

## YPR plot

```{r echo=FALSE}

        resYPR <- elefan_ga$results$resYPR1
        refs <- as.numeric(resYPR$df_Es)

        if(all(is.na(resYPR$SPR)) || is.null(elefan_ga$results$Lm50) || is.null(elefan_ga$results$Lm75)){

            par(mfrow=c(2,1), mar=c(1,4,0,2), oma=c(4,1,1,0))
            ## YPR
            plot(resYPR$FM_change, resYPR$totY, ty='n',
                 ylim = c(0,1.25) * range(resYPR$totY),
                 xaxt = "n",
                 xlab = "", ylab = "")
            tmp <- resYPR$totY[which.min(abs(resYPR$FM_change-refs[1]))]
            segments(refs[1], -10, refs[1], tmp,
                     lty=2, lwd=1.5, col="grey60")
            segments(-10, tmp, refs[1], tmp,
                     lty=2, lwd=1.5, col="grey60")
            tmp <- resYPR$totY[which.min(abs(resYPR$FM_change-refs[2]))]
            segments(refs[2], -10, refs[2], tmp,
                     lty=3, lwd=1.5, col="grey60")
            segments(-10, tmp, refs[2], tmp,
                     lty=3, lwd=1.5, col="grey60")
            lines(resYPR$FM_change, resYPR$totY, lwd=2.5,
                  col="dodgerblue2")
            legend("topleft",legend=as.expression(bquote(bold("A"))),
                   x.intersp = -0.3, y.intersp = 0.3, cex=1.3, bg= "white")
            legend("topright",legend=c("Fmax","F0.1"),
                   title = "Reference points",
                   lty = c(2,3), cex=1.1, bg= "white")
            mtext("Yield per recruit", 2, 3.5)
            ## BPR
            plot(resYPR$FM_change, resYPR$meanB, ty='n',
                 ylim = c(0,1.1) * range(resYPR$meanB),
                 xlab = "", ylab = "")
            tmp <- resYPR$meanB[which.min(abs(resYPR$FM_change-refs[3]))]
            segments(refs[3], -10, refs[3], tmp,
                     lty=2, lwd=1.5, col="grey60")
            segments(-10, tmp, refs[3], tmp,
                     lty=2, lwd=1.5, col="grey60")
            lines(resYPR$FM_change, resYPR$meanB, lwd=2.5,
                  col="dodgerblue2")
            legend("topleft",legend=as.expression(bquote(bold("B"))),
                   x.intersp = -0.3, y.intersp = 0.3, cex=1.3, bg= "white")
            legend("topright",title = "Reference points",
                   legend=c("F0.5"), lty = c(2), cex=1.1, bg= "white")
            mtext("Biomass per recruit", 2, 3.5)
            mtext("Fishing mortality", 1, 3)
            box()


        }else{

            par(mfrow=c(3,1), mar=c(1,4,0,2), oma=c(4,1,1,0))
            ## YPR
            plot(resYPR$FM_change, resYPR$totY, ty='n',
                 ylim = c(0,1.25) * range(resYPR$totY),
                 xaxt = "n",
                 xlab = "", ylab = "")
            tmp <- resYPR$totY[which.min(abs(resYPR$FM_change-refs[1]))]
            segments(refs[1], -10, refs[1], tmp,
                     lty=2, lwd=1.5, col="grey60")
            segments(-10, tmp, refs[1], tmp,
                     lty=2, lwd=1.5, col="grey60")
            tmp <- resYPR$totY[which.min(abs(resYPR$FM_change-refs[2]))]
            segments(refs[2], -10, refs[2], tmp,
                     lty=3, lwd=1.5, col="grey60")
            segments(-10, tmp, refs[2], tmp,
                     lty=3, lwd=1.5, col="grey60")
            lines(resYPR$FM_change, resYPR$totY, lwd=2.5,
                  col="dodgerblue2")
            legend("topleft",legend=as.expression(bquote(bold("A"))),
                   x.intersp = -0.3, y.intersp = 0.3, cex=1.3, bg= "white")
            legend("topright",legend=c("Fmax","F0.1"),
                   title = "Reference points",
                   lty = c(2,3), cex=1.1, bg= "white")
            mtext("Yield per recruit", 2, 3.5)
            ## BPR
            plot(resYPR$FM_change, resYPR$meanB, ty='n',
                 ylim = c(0,1.1) * range(resYPR$meanB),
                 xaxt = "n",
                 xlab = "", ylab = "")
            tmp <- resYPR$meanB[which.min(abs(resYPR$FM_change-refs[3]))]
            segments(refs[3], -10, refs[3], tmp,
                     lty=2, lwd=1.5, col="grey60")
            segments(-10, tmp, refs[3], tmp,
                     lty=2, lwd=1.5, col="grey60")
            lines(resYPR$FM_change, resYPR$meanB, lwd=2.5,
                  col="dodgerblue2")
            legend("topleft",legend=as.expression(bquote(bold("B"))),
                   x.intersp = -0.3, y.intersp = 0.3, cex=1.3, bg= "white")
            legend("topright",legend=c("F0.5"),
                   title = "Reference points",
                   lty = c(2), cex=1.1, bg= "white")
            mtext("Biomass per recruit", 2, 3.5)
            ## SPR
            plot(resYPR$FM_change, resYPR$SPR, ty='n',
                 ylim = c(0,1.1) * range(resYPR$SPR),
                 xlab = "", ylab = "")
            tmp <- resYPR$SPR[which.min(abs(resYPR$FM_change-refs[4]))]
            segments(refs[4], -10, refs[4], tmp,
                     lty=2, lwd=1.5, col="grey60")
            segments(-10, tmp, refs[4], tmp,
                     lty=2, lwd=1.5, col="grey60")
            tmp <- resYPR$SPR[which.min(abs(resYPR$FM_change-refs[5]))]
            segments(refs[5], -10, refs[5], tmp,
                     lty=3, lwd=1.5, col="grey60")
            segments(-10, tmp, refs[5], tmp,
                     lty=3, lwd=1.5, col="grey60")
            tmp <- resYPR$SPR[which.min(abs(resYPR$FM_change-refs[6]))]
            segments(refs[6], -10, refs[6], tmp,
                     lty=4, lwd=1.5, col="grey60")
            segments(-10, tmp, refs[6], tmp,
                     lty=4, lwd=1.5, col="grey60")
            lines(resYPR$FM_change, resYPR$SPR, lwd=2.5,
                  col="dodgerblue2")
            legend("topleft",legend=as.expression(bquote(bold("C"))),
                   x.intersp = -0.3, y.intersp = 0.3, cex=1.3, bg= "white")
            legend("topright",legend=c("F30","F35","F40"),
                   title = "Reference points",
                   lty = c(2,3,4), cex=1.1, bg= "white")
            mtext("Spawning potential ratio", 2, 3.5)
            mtext("Fishing mortality", 1, 3)
            box()
        }
```

```{r echo=FALSE,results='asis'}
        if(is.null(elefan_ga$results$Lm50) || is.null(elefan_ga$results$Lm75)){
            cat("<p> **Figure 6**: Yield per recruit (A) and biomass per recruit (B) for a range of fishing mortality rates (x axis). Grey segements indicate various reference points: Fmax is defined as the fishing mortality (F) leading to the maximum yield per recruit. F0.1 corresponds to F where the slope of the yield per recruit curve is equal to 10% of the slope in the origin and poses a more conservative reference point than Fmax. F0.5 corresponds to F where the biomass per recruit is equal to 50% of the biomass per recruit without fishing. </p>")
        }else{
            cat("<p> **Figure 6**: Yield per recruit (A) and biomass per recruit (B), as well as spawning potential ratio (C) for a range of fishing mortality rates (x axis). Grey segements indicate various reference points: Fmax is defined as the fishing mortality (F) leading to the maximum yield per recruit. F0.1 corresponds to F where the slope of the yield per recruit curve is equal to 10% of the slope in the origin and poses a more conservative reference point than Fmax. F0.5 corresponds to F where the biomass per recruit is equal to 50% of the biomass per recruit without fishing. F30, F35, and F40 correspond to F that leads to a SPR of 30%, 35%, and 40% respectively.</p>")
        }
```

## YPR-Isopleth plot

```{r echo=FALSE}
        par(mfrow = c(2,1), mar = c(4,4,0,1), oma = c(2,0,1,0))
        plot_predict_mod(elefan_ga$results$resYPR2,
                         type = "Isopleth", xaxis1 = "FM",
                         mark = TRUE, contour = 6, xlab="",
                         ylab1 = "")
        mtext(expression(L[50]),2,2.5)
        legend("topleft",legend=as.expression(bquote(bold("A"))),
               x.intersp = -0.3, y.intersp = 0.3, cex=1.3, bg = "white")
        plot_predict_mod(elefan_ga$results$resYPR2, type = "Isopleth",
                         xaxis1 = "FM", yaxis1 = "B_R", mark = TRUE,
                         contour = 6, xlab = "Fishing mortality",
                         ylab1 = "")
        mtext(expression(L[50]),2,2.5)
        legend("topleft",legend=as.expression(bquote(bold("B"))),
               x.intersp = -0.3, y.intersp = 0.3, cex=1.3,
               bg = "white")
```

```{r echo=FALSE,results='asis'}
        cat("<p> **Figure 7**: Yield (A) and biomass (B) per reruit for a range of fishing mortality rates and gear selectivity combinations. Colors indicate high (red) to low (blue) yield and biomass. Gear selectivity is defined by the length at 50% selectivity (L50). The black dot indicates current yield and biomass per recruit.</p>")
```


## Growth parameter table

```{r echo=FALSE}
        tmp <- as.data.frame(c(elefan_ga$results$resGA$par,
                               list(Rn_max = elefan_ga$results$resGA$Rn_max)))
        names(tmp) <- replace(names(tmp), names(tmp)=="t_anchor", "ta")
        names(tmp) <- replace(names(tmp), names(tmp)=="Rn_max", "Rn")
        names(tmp) <- replace(names(tmp), names(tmp)=="phiL", "phi'")
        kable(tmp)
```


```{r echo=FALSE,results='asis'}
        cat(paste0("<p> **Table 1**: Estimated von Bertlanffy growth parameters (","\\(L_\\infty, K, t_a\\)","), the growth performance coefficient ","\\(phi' = \\log_{10} K + 2 \\log_{10} L_\\infty\\)",", and the best score value (","\\(Rn\\)","). Phi' provides a metric that accounts for the correlation of ","\\(L_\\infty\\)"," and ","\\(K\\)"," to compare growth parameters among analyses or species. The Rn value allows comparison of the fit of estimated growth parameters to the data set for different MA values, growth paramater search spaces, or ELEFAN optimisation parameters (e.g. population size), but not for different data sets or bin sizes.</p>"))
```

## Mortality rates

```{r echo=FALSE}

        Z <- elefan_ga$results$resCC$Z
        M <- elefan_ga$results$resM
        FM <- Z - M
        E <- FM / Z
        tmp <- as.data.frame(t(as.matrix(c(Z, M, FM, E,
                                           elefan_ga$results$L50,
                                           elefan_ga$results$L75))))
        names(tmp) <- c("Z","M","F","E","L50","L75")
        kable(tmp)
```
        
```{r echo=FALSE,results='asis'}
        if(input$select == "Estimate" || (input$l50_user == 0 && input$l75_user == 0) || (input$l50_user == 0 && input$wqs_user == 0)){
            cat("<p> **Table 2**: Estimated mortality rates (Z, F, M), exploitation rate (E), and estimated selectivity parameters (L50, L75).</p>")
        }else{
            cat("<p> **Table 2**: Estimated mortality rates (Z, F, M), exploitation rate (E), and provided selectivity parameters (L50, L75).</p>")
        }
```
        
## Reference points

```{r echo=FALSE}
        if(is.null(elefan_ga$results$Lm50) || is.null(elefan_ga$results$Lm75)){
            tmp <- elefan_ga$results$resYPR1$df_Es[1:3]
            names(tmp) <- c("Fmax","F0.1","F0.5")
            kable(tmp)
        }else{
            tmp <- elefan_ga$results$resYPR1$df_Es
            names(tmp) <- c("Fmax","F0.1","F0.5","F30","F35","F40")
            kable(tmp)
        }
```

```{r echo=FALSE,results='asis'}
        if(is.null(elefan_ga$results$Lm50) || is.null(elefan_ga$results$Lm75)){
            cat("<p> **Table 3**: Estimated reference points (Fmax, F0.1, F0.5).</p>")
        }else{
            cat("<p> **Table 3**: Estimated reference points (Fmax, F0.1, F0.5) and SPR-based reference points (F30, F35, F40).</p>")
        }
```


## Stock status table
```{r echo=FALSE}
        Z <- elefan_ga$results$resCC$Z
        M <- elefan_ga$results$resM
        FM <- Z - M
        if(is.null(elefan_ga$results$Lm50) || is.null(elefan_ga$results$Lm75)){
            tmp <- cbind(FM/elefan_ga$results$resYPR1$df_Es[1:3])
            names(tmp) <- c("F/Fmax","F/F0.1","F/F0.5")
            kable(tmp)
        }else{
            tmp <- cbind(FM/elefan_ga$results$resYPR1$df_Es,
                         elefan_ga$results$resYPR1$currents$curr.SPR)
            names(tmp) <- c("F/Fmax","F/F0.1","F/F0.5","F/F30","F/F35","F/F40","SPR")
            kable(tmp)
        }
```
    
```{r echo=FALSE,results='asis'}
        if(is.null(elefan_ga$results$Lm50) || is.null(elefan_ga$results$Lm75)){
            cat("<p> **Table 4**: Estimated stock status in terms of current fishing mortality (F) to reference points (Fmax, F0.1, F0.5).</p>")
        }else{
            cat("<p> **Table 4**: Estimated stock status in terms of current fishing mortality (F) to reference points (Fmax, F0.1, F0.5, F30, F35, F40) and current Spawning Potential Ratio (SPR).</p>")
        }
```

******
## Data settings

  **Input File** : `r input$fileGa$name`

  **Selected year(s) for analysis** : `r input$ELEFAN_years_selected`

  **Aggregation method** : `r input$ELEFAN_agg` 

  **Bin Size** : `r input$ELEFAN_GA_binSize` 

  **Moving Average (MA)** : `r input$ELEFAN_GA_MA` 

  **Additional squareroot transformation ?** : `r if(!is.null(input$ELEFAN_GA_addl.sqrt)){if(input$ELEFAN_GA_addl.sqrt){"Yes"}else{"No"}}else{"No"}`

## Search space for growth parameters

  **Asymptotic length(Linf)** : `r min(input$ELEFAN_GA_Linf)` to `r max(input$ELEFAN_GA_Linf)`

  **Growth rate (K)** : `r min(input$ELEFAN_GA_K)` to `r max(input$ELEFAN_GA_K)` 

  **Time anchor(ta)** : `r min(input$ELEFAN_GA_t_anchor)` to `r max(input$ELEFAN_GA_t_anchor)`

  **Seasonal model?** : `r if(!is.null(input$ELEFAN_GA_seasonalised)){if(input$ELEFAN_GA_seasonalised){"Yes"}else{"No"}}else{"No"}`

  `r if(!is.null(input$ELEFAN_GA_seasonalised)){if(input$ELEFAN_GA_seasonalised){paste0("**Amplitude (C)** : ", min(input$ELEFAN_GA_C)," to ",max(input$ELEFAN_GA_C))}else{}}else{}`

  `r if(!is.null(input$ELEFAN_GA_seasonalised)){if(input$ELEFAN_GA_seasonalised){paste0("**Summer point (ts)** : ",min(input$ELEFAN_GA_ts)," to ",max(input$ELEFAN_GA_ts))}else{}}else{}`

## ELEFAN's genetic algorithm

  **Population size**: `r input$ELEFAN_GA_popSize`

  **Maximum number of generations** : `r input$ELEFAN_GA_maxiter`

  **Number of generations without improvement** : `r input$ELEFAN_GA_run`

  **Probability of mutation** : `r input$ELEFAN_GA_pmutation`

  **Probability of crossover** : `r input$ELEFAN_GA_pcrossover`

  **Degree of elitism** : `r input$ELEFAN_GA_elitism`
  
## Stock status

 **Selected years** : `r input$ELEFAN_years_selected_cc`
 
 **Length-weight relationship** : `r paste0("\\(W = a \ L^{b}\\)"," with a=",input$LWa," and b=",input$LWb)`
 
 **Natural Mortality**  
 
    Method : `r input$natM`
    
    `r if(input$natM =="Pauly's growth & temp. formula"){paste0("Average ambient sea surface temperature : ",input$temp)}`
    
    `r if(input$natM =="Pauly's growth & temp. formula"){paste0("Correction for schooling? : ",if(!is.null(input$schooling)){if(input$schooling){"Yes"}else{"No"}}else{"No"})}`
    
    `r if(input$natM =="Pauly's growth & temp. formula"){paste0("Maximum age : ",input$tmax)}`
    
    
 **Maturity** 
 
    Lm50 : `r input$Lm50` 
    
    Lm75 : `r input$Lm75` 
 
 **Selectivity** 
 
    Selectivity : `r input$select`
    
    `r if(input$select =="Define L50 & L75"){paste0("L50 (user defined) : ",input$l50_user)}`
    
    `r if(input$select =="Define L50 & L75"){paste0("L75 (user defined) : ",input$l75_user)}`
    
    `r if(input$select =="Define L50 & (L75-L25)"){paste0("width (L75 - L25; user defined) : ",input$wqs_user)}`
    
  **Prediction range**
  
    Fishing mortality :`r paste0("Steps:",input$fRangeSteps,", min:" ,input$fRangeMin,', max:', input$fRangeMax)`
    
    Length at 50% selectivity (L50) : `r paste0("Steps:",input$lcRangeSteps,if(input$select!="Estimate"){paste0(", min:" ,input$lcRangeMin,', max:', input$lcRangeMax)}else{""})`
    
    
******