---
title: "ELEFAN_GA Report"
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

> Electronic LEngth Frequency ANalysis for estimating growth parameter

## Raw LFQ data
```{r echo=FALSE}
plot(elefan$results$plot1, Fname = "catch", date.axis = "modern")
```

## Recontructed LFQ data
```{r echo=FALSE}
plot(elefan$results$plot2, Fname = "rcounts", date.axis = "modern")
```

## Results of the computation

```{r echo=FALSE}
plot(elefan$results$data)
```

## Thompson and Bell model with changes in F
```{r echo=FALSE}
plot(elefan$results$plot3, mark = TRUE)
mtext("(a)", side = 3, at = -1, line = 0.6)
```

## Thompson and Bell model with changes in F and Lc
```{r echo=FALSE}
plot(elefan$results$plot4, type = "Isopleth", xaxis1 = "FM", mark = TRUE, contour = 6)
mtext("(b)", side = 3, at = -0.1, line = 0.6)
```


******


**Highest value of fitness function:** `r elefan$results$data$Rn_max`

**Length infinity ( $L_\infty$ in cm ):** `r elefan$results$data$par$Linf`

**Curving coefficient (K):** `r elefan$results$data$par$K`

**Time point anchoring growth curves in year-length coordinate system, corresponds to peak spawning month (t_anchor):** `r elefan$results$data$par$t_anchor`

**Amplitude of growth oscillation (NOTE: only if 'Seasonalized' is checked; C):** `r elefan$results$data$par$C`

**Winter point of oscillation ($t_w$)**

**Summer point of oscillation (NOTE: only if 'Seasonalized' is checked; $ts$=$t_w$-0.5):** `r elefan$results$data$par$ts`

**Growth performance index defined as phiL = log10(K) + 2 * log10(Linf):** `r elefan$results$data$par$phiL`

**Biological reference levels:**
```{r echo=FALSE, results='asis'}
df1 <- as.data.frame(elefan$results$plot3$df_Es)
knitr::kable(df1, digits = 2, align=rep('c', 5))
```

**Current yield and biomass levels:**
```{r echo=FALSE, results='asis'}
CURR_GA<-elefan$results$plot3$current
CURR_GA<-CURR_GA[,-7]
names(CURR_GA)<-c("Length-1st-capture(Lc)", "Age-1st-capture(tc)", "Effort","Fishing mortality", "Catch", "Yield", "Biomass")
df2 <- as.data.frame(CURR_GA)
knitr::kable(df2, digits = 2, align=rep('c', 5))
```

******
## Input parameters  
Input File: `r input$fileElefan$name`  
Seasonalized: `r input$ELEFAN_SA_seasonalised`  
  
**Optional Parameters**  
Linf fix: `r input$ELEFAN_Linf_fix`  
Linf range: `r input$elefan_linf_range`  
K range: `r input$elefan_k_range`  
C: `r input$ELEFAN_C`  
MA: `r input$ELEFAN_MA`  
Age max: `r input$ELEFAN_agemax`  
ContourL `r if(input$ELEFAN_contour){"TRUE"}else{"FALSE"}`  
sqrt: `r if(input$ELEFAN_GA_addl.sqrt){"TRUE"}else{"FALSE"}`  
Plus group: `r input$ELEFAN_GA_PLUS_GROUP`  

******
## Dataset
Synthetic length-frequency data as generated by the function lfqGen from the fishdynr package (Taylor 2016). Can be used by ELEFAN, ELEFAN_SA, or ELEFAN_GA. The data is generated with the following von Bertalanffy growth parameters:

* K = 0.2 +/- 0.1 (CV)

* Linf = 123 +/- 0.05 (CV)

* C = 0.3

* ts = 0

* t_anchor between 0.16 and 0.34 (Time when yearly recruitment pulse occurs; e.g. 0 = Jan 1, 0.25 = Apr 1, 0.5 = Jul 1, 0.75 = Oct 1; repro_wt = c(0, 0, 0.2, 1, 0.6, 0, 0, 0, 0, 0, 0, 0))