---
title: "ELEFAN_SA Report"
output: pdf_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

> Electronic LEngth Frequency ANalysis with simulated annealing for estimating growth parameters

## Raw LFQ data
```{r echo=FALSE}
plot(elefan_sa$results$plot1, Fname = "catch", date.axis = "modern")
```

## Recontructed LFQ data
```{r echo=FALSE}
plot(elefan_sa$results$plot2, Fname = "rcounts", date.axis = "modern")
```

#Results of the computation

```{r echo=FALSE}
plot(elefan_sa$results$data)
```

##Thompson and Bell model with changes in F
```{r echo=FALSE}
plot(elefan_sa$results$plot3, mark = TRUE)
mtext("(a)", side = 3, at = -1, line = 0.6)
```

##Thompson and Bell model with changes in F and Lc
```{r echo=FALSE}
plot(elefan_sa$results$plot4, type = "Isopleth", xaxis1 = "FM", mark = TRUE, contour = 6)
mtext("(b)", side = 3, at = -0.1, line = 0.6)
```


******


**Highest value of fitness function:** `r elefan_sa$results$data$Rn_max`


**Length infinity in cm:** `r elefan_sa$results$data$par$Linf`

**Curving coefficient:** `r elefan_sa$results$data$par$K`

**Time point anchoring growth curves in year-length coordinate system, corrsponds to peak spawning month:** `r elefan_sa$results$data$par$t_anchor`

**Amplitude of growth oscillation:** `r elefan_sa$results$data$par$C`

**Summer point of oscillation (ts = WP - 0.5):** `r elefan_sa$results$data$par$ts`

**Growth performance index defined as phiL = log10(K) + 2 * log10(Linf):** `r elefan_sa$results$data$par$phiL`

******
##Dataset
Synthetic length-frequency data as generated by the function lfqGen from the fishdynr package (Taylor 2016). Can be used by ELEFAN, ELEFAN_SA, or ELEFAN_GA. The data is generated with the following von Bertalanffy growth parameters:

* K = 0.2 +/- 0.1 (CV)

* Linf = 123 +/- 0.05 (CV)

* C = 0.3

* ts = 0

* t_anchor between 0.16 and 0.34 (Time when yearly recruitment pulse occurs; e.g. 0 = Jan 1, 0.25 = Apr 1, 0.5 = Jul 1, 0.75 = Oct 1; repro_wt = c(0, 0, 0.2, 1, 0.6, 0, 0, 0, 0, 0, 0, 0))